\documentclass{screenplay}[2012/06/30]
\title{DEA}
\author{Andrés Rodarte López}
\address{Av. Alfredo V. Bonfil\\
CDMX, Coyoacán 04480\\
777-327-4458\\
andres.rodarte.\\
lopez@gmail.com\\}
\begin{document}
\coverpage
\intslug[unknown]{Darkness room}
DEA opens her eyes (camera view) and everything is dark. 
The furniture in the room is barely visible.
She sits up and see her body in a nightgown. 
She looks around, not fully knowing where she is,
only few thing in a room could been seen, we mostly see her under a bed sheet. 
When looking to the right a dimming light shows up in a door's silhouette. 
DEA stands up, and proceeds to walk towards the light, in hopes of finding a
way out. A lock of her hair slides in front of her eyes as she walks.
\begin{dialogue}[Slightly Breathing]{DEA}
    ...
\end{dialogue}
DEA reaches the door, takes the metallic doorknob with caution and opens it as she 
does that the light starts to die, like the light as you go into the deeps of the ocean. 
\intercut
\intslug[night]{Forest room}
DEA, how is again in her bed, looking at the roof, takes her hand and removes the excess of sweat in her forehead. 
She looks at her palm, which is really wet.
\begin{dialogue}[Slightly Groaning]{DEA}
    ...
\end{dialogue}
DEA holds her stomach with both arms, not in pain both with discomfort. She looks up,
looking to the right side, she sees the bathroom door. DEA stands up, the floor is full of 
dry leaves.
\begin{dialogue}[Surpise sound]{DEA}
    ...
\end{dialogue}
DEA breaks the leaves with her first foot step. 
The environment starts to get wet, and the 
smell reassembles the smell of wet mud.
\begin{dialogue}[Makes long sniffs]{DEA}
    ...
\end{dialogue}
DEA walks towards the door, she's looking at her feet, seeing the leaves and as she
get close to the door, she starts to see the path in front of her. 
Being at the door, she looks its frame.
A lizard is walking upwards the frame that has some roots ends. At the same time DEA is opening the door and 
getting in, not seeing that the room is in complete darkness and without floor. 
She steps in and starts to fall into the darkness.
\begin{dialogue}[Breathing in terror]{DEA}
    ...
\end{dialogue}
DEA looks around, nothing is visible, even her arms, that are extended, are barely visible.
DEA starts to hug her self and putting her body in fetal position while, falling. The sound of air is
intensifying and she closes her eyes.
\begin{dialogue}[Making a sound with her trout]{DEA}
    ...gulp...
\end{dialogue}
\intercut
\intslug[night]{Winter room}
DEA wakes up in a closet. She opens her eyes and sees her knees, she is the fetal position.
She rises her head and take the look up and 
sees some clothes hanging. In the floor some shoes.
\begin{dialogue}[Exhalates]{DEA}
    ...
\end{dialogue}
The breath of DEA is visible to her, she looks at her hands and
the tips of her fingers get a rose tone. Then, she opens the door and
crawl out, as she goes out she starts to stand up. She locks at her hands
a warm color is getting visible in her skin. Between her hands she sees
a body in her bed. She get close to she. Locks first at her legs, slowly 
going up, admiring her.
\begin{dialogue}[Shock sound]{DEA}
    ...
\end{dialogue}
DEA realize the person in the bed is she. 
She outline her face features, the colors get little shiners. She stops her hand at her left cheek.
She can hear her beat accelerating as she 
gets closer and closer to herself, until she finally close her eyes looking at her face,
she kiss her.
\intercut
\intslug[moorning]{DEA rooms}
DEA opens her eyes, she is in her bed, now looking to her window.
The light of the new day came inside in beams of light. she sits up and stretch her body,
waking up jumping out of bed, as she does this her foot crushes a single brown leave
\begin{dialogue}[Shock sound]{DEA}
    ...
\end{dialogue}
DEA takes her foot up to her and takes the leave out of her foot, looks at it
closely and put in a piece of furniture. She moves to the bathroom. As she opens the door
and jumps back, like a reflection, she looks at the floor and enters.
\begin{dialogue}[Laughfing]{DEA}
    ...
\end{dialogue}
She reaches the sink. The mirror that is in the cabin above it is open.
DEA opens the water flow, and washes her faces. She opens her eyes, as she is closing the mirror door,
she stops a little in a midway, to se her face, she completely close it, and smile.
\end{document}